\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-24 paper.tex
WIP intro

\title{\LARGE \bf
{\tt underworlds}: Cascading Situation Assessment for Robots
}

@@

Representing \emph{alternative states} is actually often critical, as shown by
the following exemplary situation: software components manipulating environment
models typically perform better if the models are physically consistent.
However, low-level perception inaccuracies often introduce hard-to-avoid
physical inconsistencies (like objects floating in the air, or on the contrary
wrongly inset into other objects). Therefore, a post-process stage (for
instance, using a physics simulation engine) might be desired to correct the
positions of the objects seen by the robot. Implemented with a classical approach using ROS TF
frames, we would see an object {\tt book} located at the origin of the reference
frame {\tt book\_frame}, and a secondary frame {\tt book\_frame\_corrected} computed by the
physics engine. It is easy to see why such an approach would be quickly
confusing (where is my book?) and would not scale well, with the robot's 3D
model cluttered with spurious frames.

; efficiently sharing a dynamic 3D scene is
even more difficult;  bserving a scene from
different viewpoints to compute visibility is not directly possible

One of the main features of \uwds is the ability to store many parallel
worlds: past models of the environment, future models, models with some objects
filtered out, models that are physically consistent, etc.

This package provides the \uwds server, a Python client library, and a set
of tools to interact with the system (viewers, scene loader, etc.).

A handful of useful example applications are also provided, like skeleton
tracking (using OpenNI) or visibility tracking.

@@

>>>>

\title{\LARGE \bf
Cascading Situation Assessment for Robots
}

@@

Representing \emph{alternative states} is actually often critical. For instance,
software components manipulating environment models typically perform better if
the models are physically consistent. However, low-level perception inaccuracies
at the sensor level often introduce hard-to-avoid physical inconsistencies (like
detected objects floating in the air, or on the contrary wrongly inset into
other objects). Therefore, a post-process stage (for instance, using a physics
simulation engine) might be desired to move the objects seen
by the robot into physically-correct positions. Implemented with a classical
approach (for instance, using ROS TF frames), we would get an object {\tt book}
located at the frame {\tt book\_frame}, and a secondary frame {\tt
book\_frame\_corrected} computed by the physics engine. It is easy to see why
such an approach would be quickly confusing (where is in fact my book?) and would not
scale well, with the robot's 3D model cluttered with spurious frames.

Another relevant example pertains to geometric task planning: a geometric task
planner typically need to reason over hypothetical future states of the
environment (``what happen if I move this glass onto that pile of books?'').
The planner might want to quickly generate possible future states, that
themselves might require further processing (for instance, running a physics
simulation). This use-case evidences the need for a flexible representation
system, where models are derived from each others, with partial modifications
and different timescales.

@@

serving a scene from
different viewpoints to compute visibility is not directly possible
